# {.title-slide background-image="img/hi/background/v1.jpg" background-size="cover" background-position="center"}

::: {.title-highlight}
{{< meta event.title >}}
:::

::: {.subtitle-highlight}
{{< meta event.subtitle >}}

:::

::: {.title-meta}
<a href="https://hi.is/staff/{{< meta presenter.username >}}" target="_blank" rel="noopener noreferrer"><strong>{{< meta presenter.name >}}</strong></a>
<a href="https://orcid.org/{{< meta presenter.orcid >}}" target="_blank" rel="noopener noreferrer"><i class="fa-brands fa-orcid" aria-hidden="true"></i></a>
<a href="mailto:{{< meta presenter.username >}}@hi.is"><i class="fa-solid fa-envelope" aria-hidden="true"></i> {{< meta presenter.username >}}@hi.is</a>
:::

::: {.event-meta}
{{< meta event.name >}}: {{< meta event.date >}}
:::

## What This Template Shows

- Standard slide layouts
- R code and plots
- LaTeX notation
- Tables, quotes, and callouts
- Background colors and background figures
- Speaker notes


# Core Slide Patterns

## Bullets

Use short lines and let the slide carry one idea.

- First point
- Second point
- Third point

::: notes
Speaker notes go inside a `notes` block. Press `S` in Reveal.js to open presenter view.
:::

## Incremental Bullets

Use `.incremental` when the order matters.

::: incremental
- Define the question
- Show the data
- Fit the model
- Interpret the result
:::

## Two Columns

:::: {.columns}

::: {.column width="45%"}
### Left

- Methods
- Assumptions
- Data source
:::

::: {.column width="55%"}
### Right

Use this side for a figure, table, equation, or code output.

::: {.callout}
Keep one main comparison per slide.
:::
:::

::::

## Callouts And Quotes

::: {.callout}
Use a callout for the sentence you want people to remember.
:::

> A short quote can work well when it frames a result or motivates a section.

# R Examples

## R Code

```{r}
summary(cars)
```

## Base R Plot

```{r}
#| label: fig-base-r
#| fig-cap: "A simple base R plot."
#| fig-width: 7
#| fig-height: 4.2
plot(
  cars$speed,
  cars$dist,
  pch = 19,
  col = "#10099F",
  xlab = "Speed",
  ylab = "Stopping distance",
  main = "Cars data"
)
grid(col = "#E8E8E8")
```

## R Plot With Hidden Code

```{r}
#| label: fig-hidden-code
#| echo: false
#| fig-width: 7
#| fig-height: 4.2
set.seed(2026)
x <- rnorm(300)
hist(
  x,
  breaks = 24,
  col = "#2DD2C0",
  border = "white",
  main = "Distribution of simulated values",
  xlab = "Value"
)
```

## Optional ggplot2 Pattern

Set `eval: true` when `ggplot2` is installed.

```{r}
#| eval: false
#| fig-width: 7
#| fig-height: 4.2
library(ggplot2)

ggplot(cars, aes(speed, dist)) +
  geom_point(color = "#10099F", size = 3) +
  geom_smooth(method = "lm", se = false, color = "#EB7125") +
  labs(x = "Speed", y = "Stopping distance") +
  theme_minimal(base_size = 18)
```

# Math And Tables

## LaTeX Notation

Inline math works like this: $\hat{\beta}_1$ estimates the slope.

Display equations work like this:

$$
y_i = \beta_0 + \beta_1 x_i + \epsilon_i,\qquad
\epsilon_i \sim \mathcal{N}(0, \sigma^2)
$$

## Model Summary Slide

| Quantity | Meaning | Example |
|---|---|---:|
| $n$ | Sample size | 50 |
| $\bar{x}$ | Mean | 12.4 |
| $s$ | Standard deviation | 3.1 |

::: {.callout .accent}
Use notation on the slide, then explain the interpretation out loud.
:::

# Backgrounds

## Solid Background {background-color="#10099F" .dark-slide}

Use a slide-level background color for section breaks or key results.

::: {.big-number}
42%
:::

Main result, estimate, or headline.

## Background Figure Pattern

To use your own background image, place it in `img/`, then add a slide header like:

```markdown
## Slide Title {background-image="img/your-background.jpg" background-size="cover" .dark-slide}
```

::: {.callout}
This project is self-contained: avoid references to `tmp/` because you plan to delete it.
:::

## Figure Slide

Replace this placeholder with your own image.

::: {.figure-placeholder}
`img/your-figure.png`
:::

# Closing

## Summary

1. State the main result.
2. Connect it back to the research question.
3. Leave one concrete next step.

## Thank You

::: {.title-box}
Questions?

**your.email@example.com**
`github.com/your-user`
:::

